---
title: "HW 01 - Airbnb listings in Edinburgh"
author: "Jieming Xiao"
date: "07/12/2022"
output: github_document
---

## Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
library(dsbox)
library(ggplot2)
```

## Exercises

### Exercise 1

There are 13,245 rows in the dataset.

### Exercise 2

Each row represents a listing of properties.


### Exercise 3



```{r prices-neighbourhoods}
ggplot(data = edibnb, mapping = aes(x = price)) +
  geom_histogram(binwidth = 500) +
  facet_wrap(~neighbourhood)
```

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

```{r top-5-median}
# remove this comment and add the code for Exercise 4 here
```

```{r top-5-median-plot}
# remove this comment and add the code for Exercise 4 here
```

```{r top-5-median-summary-stats}
# remove this comment and add the code for Exercise 4 here
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r review-scores-rating}
ggplot(edibnb, aes(x = review_scores_rating,
                  fill = neighbourhood)) +
  geom_density(adjust = 7, 
               alpha = 0.5) 

```
The majority of the rating scores are beyond 80, and very few rating scores are below 60, which means guests rate properties generously in general. For neighborhoods, properties in New Town and Newington are getting the most high rating scores, while properties in the Southside and West End get less higher ratings. 
